PM Component Paper Plots

### 2021-10-07 code/data-viz/forest-plots-color.Rmd
revision

```{r Load data}
load(here('output','analysis','out-pmc-base.RDa'))
load(here('output','analysis','out-pmc-ses.RDa'))
load(here('output','analysis','out-fac-base.RDa'))
load(here('output','analysis','out-fac-ses.RDa'))
load(here('output','analysis','out-fac-base-ec.RDa'))
load(here('output','analysis','out-fac-ses-ec.RDa'))
load(here('output','analysis','out-pmc-resid.RDa'))
load(here('output','analysis','out-fac-resid.RDa'))
load(here('output','analysis','out-pmc-age.RDa'))
load(here('output','analysis','out-fac-age.RDa'))
load(here('output','analysis','out-pmc-sex.RDa'))
load(here('output','analysis','out-fac-sex.RDa'))
load(here('output','analysis','out-pmc-race.RDa'))
load(here('output','analysis','out-fac-race.RDa'))
load(here('output','analysis','out-pmc-urbanicity.RDa'))
load(here('output','analysis','out-fac-urbanicity.RDa'))
load(here('output','analysis','out-pmc-sescat.RDa'))
load(here('output','analysis','out-pmc-region.RDa'))
load(here('output','analysis','out-pmc-resid-region.RDa'))
load(here('output','analysis','out-fac-region.RDa'))
load(here('output','analysis','out-pmc-brfss.RDa'))
load(here('output','analysis','out-pmc-buffer.RDa'))
load(here('output','analysis','out-pmc-expo.RDa'))
```

@@

@@

plot.labs <- c("24-miles", "12-miles", "6-miles") 
plot.cols <- c("#EB2226", "#075AAA", "#01742F")

@@

>>>>

```{r Load data}
load(here('output','analysis','out-pmc-base.RDa'))
load(here('output','analysis','out-pmc-ses.RDa'))
load(here('output','analysis','out-fac-base.RDa'))
load(here('output','analysis','out-fac-ses.RDa'))
load(here('output','analysis','out-fac-base-ec.RDa'))
load(here('output','analysis','out-fac-ses-ec.RDa'))
load(here('output','analysis','out-pmc-resid.RDa'))
load(here('output','analysis','out-fac-resid.RDa'))
load(here('output','analysis','out-pmc-age.RDa'))
load(here('output','analysis','out-fac-age.RDa'))
load(here('output','analysis','out-pmc-sex.RDa'))
load(here('output','analysis','out-fac-sex.RDa'))
load(here('output','analysis','out-pmc-race.RDa'))
load(here('output','analysis','out-fac-race.RDa'))
load(here('output','analysis','out-pmc-urbanicity.RDa'))
load(here('output','analysis','out-fac-urbanicity.RDa'))
load(here('output','analysis','out-pmc-sescat.RDa'))
load(here('output','analysis','out-pmc-region.RDa'))
load(here('output','analysis','out-pmc-resid-region.RDa'))
load(here('output','analysis','out-fac-region.RDa'))
load(here('output','analysis','out-pmc-brfss.RDa'))
load(here('output','analysis','out-pmc-buffer.RDa'))
load(here('output','analysis','out-pmc-expo.RDa'))
load(here('output','analysis','out-pmc-buffer-expo.RDa'))
```

@@

```{r set theme 4 - matrix plots}
ggtheme.matrix <- theme_bw() + 
  theme(panel.spacing.x = unit(0.25, 'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 9, color = 'black'),
        legend.position = 'right',
        legend.title = element_blank(),
        legend.text = element_text(size = 9, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')
  )
```

@@

plot.labs <- c("24-mile", "12-mile", "6-mile") 
plot.cols <- c("#EB2226", "#075AAA", "#01742F")

@@

```{r Components Buffer & Exposure window}
dt <- out.pmc.buffer.expo %>% 
  arrange(Buffer, Window) %>% 
  mutate(Cause = factor(Cause, levels = rev(cuz)),
         Buffer = ifelse(Buffer == 6, "6-mile",
                         ifelse(Buffer == 12, "12-mile", "24-mile")),
         Buffer = factor(Buffer, levels = c("6-mile", "12-mile", "24-mile")),
         Window = ifelse(Window == 1, "1-yr",
                         ifelse(Window == 2, "2-yr",
                                ifelse(Window == 3, "3-yr",
                                       ifelse(Window == 4, "4-yr", "5-yr")))),
         Window = as.factor(Window),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16))) #1-null # 16-sigpos

Plot.Matrix(dt = dt, cmp = "SO4", title = expression(SO[4]^"2-"), 
            ggtheme = ggtheme.matrix) +
ggsave(here('output', 'plot','SO4-buffer-expo.png'), width = 9, height = 8)

Plot.Matrix(dt = dt, cmp = "NO3", title = expression(NO[3]^"-"), 
            ggtheme = ggtheme.matrix) +
ggsave(here('output', 'plot','NO3-buffer-expo.png'), width = 9, height = 8)

Plot.Matrix(dt = dt, cmp = "Si", title = "Si", 
            ggtheme = ggtheme.matrix) +
ggsave(here('output', 'plot','Si-buffer-expo.png'), width = 9, height = 8)
```
